### 2020-05-23 Paper/main.tex
Set up paper template

\documentclass[journal]{IEEEtran}

\usepackage[style=ieee]{biblatex} 
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{float}

% \bibliography{example_bib.bib}

\begin{document}

\title{Investigating Cross-Sectional Size Distribution of Randomly Distributed 3D Spheres}

\author{Sai Pandian, ID:\@ 29899923}%

% The report headers
\markboth{PHYS6017 Computer Techniques in Physics Report 2, May 2020}
% do not delete next lines
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

\maketitle

\begin{abstract}
  Text
\end{abstract}

\section{Introduction}

\IEEEPARstart{T}{ext}

\section{Materials and Methods}
Text

\section{Results}
Text

\begin{figure}[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{./../Figures/box3d_noplane.pdf}
\caption{Illustrations, graphs, and photographs may fit across both columns, if
  necessary. Your artwork must be in place in the article.}
\label{fig:3dplot}
\end{center}
\end{figure}

\begin{figure}[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{./../Figures/box3d.pdf}
\caption{Illustrations, graphs, and photographs may fit across both columns, if
  necessary. Your artwork must be in place in the article.}
\label{fig:3dplot_plane}
\end{center}
\end{figure}

\begin{figure}[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{./../Figures/circles.pdf}
\caption{Illustrations, graphs, and photographs may fit across both columns, if
  necessary. Your artwork must be in place in the article.}
\label{fig:circles}
\end{center}
\end{figure}

\begin{figure}[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{./../Figures/750_01.pdf}
\caption{Illustrations, graphs, and photographs may fit across both columns, if
  necessary. Your artwork must be in place in the article.}
\label{fig:size1}
\end{center}
\end{figure}

\begin{figure}[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{./../Figures/750_03.pdf}
\caption{Illustrations, graphs, and photographs may fit across both columns, if
  necessary. Your artwork must be in place in the article.}
\label{fig:size3}
\end{center}
\end{figure}

\begin{figure}[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{./../Figures/750_07.pdf}
\caption{Illustrations, graphs, and photographs may fit across both columns, if
  necessary. Your artwork must be in place in the article.}
\label{fig:size7}
\end{center}
\end{figure}

\begin{figure}[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{./../Figures/750_07_random.pdf}
\caption{Illustrations, graphs, and photographs may fit across both columns, if
  necessary. Your artwork must be in place in the article.}
\label{fig:random}
\end{center}
\end{figure}

\begin{figure}[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{./../Figures/750_07_NoNoise.pdf}
\caption{Illustrations, graphs, and photographs may fit across both columns, if
  necessary. Your artwork must be in place in the article.}
\label{fig:nonoise}
\end{center}
\end{figure}

\begin{figure}[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_100.pdf}
\caption{Illustrations, graphs, and photographs may fit across both columns, if
  necessary. Your artwork must be in place in the article.}
\label{fig:2noise}
\end{center}
\end{figure}

\begin{figure}[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_10.pdf}
\caption{Illustrations, graphs, and photographs may fit across both columns, if
  necessary. Your artwork must be in place in the article.}
\label{fig:1noise}
\end{center}
\end{figure}

\section{Discussion and Summary}
Text

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%
\appendices{}
\section{Appendix Name}
Text

\printbibliography{}
\end{document}

### 2020-05-24 Paper/main.tex
Completed intro and method section

@@
 
+\usepackage[caption=false]{subfig}
+\usepackage{todonotes}
+
 % \bibliography{example_bib.bib}
@@
 
-\title{Investigating Cross-Sectional Size Distribution of Randomly Distributed 3D Spheres}
+\title{Investigating Cross-Sectional Size Distribution of Randomly Distributed
+       3D Spheres}
 
@@
 
-\IEEEPARstart{T}{ext}
+\IEEEPARstart{I}{n} the world of Material Science and Crystallography, it is
+often the case that a material is identified and classified using the
+distribution of its constituent particle sizes. However, direct observation of
+the particles so as to construct a distribution is often impossible. Using a
+modern microscope or laser imaging techniques, it is possible to observe
+particles in a cross-section of material. But the observed radii of particles in
+this cross-section do not necessarily correspond directly to the radii of the
+particles in the material, since the plane of the cross-section is not
+necessarily oriented such that the observed particles lie exactly on the
+plane. Thus, it becomes difficult to relate the observed distribution of
+particle sizes in the plane to the real distribution of particle sizes in the
+material.
 
-\section{Materials and Methods}
-Text
+Mathematically, determining the distribution of spherical particles from planar
+sections is a well known problem called Wicksell's Corpuscle Problem
+\todo{cite}, named after S. D. Wicksell, who solved the problem in 1925. With
+this solution, it is possible to determine the original distribution of
+spherical particles. Thus, it is possible to determmine the distribution of
+particle sizes in a solid from its observed cross-section, allowing us to
+identify and classify materials better \todo{nasa}.
+
+In this paper we aim to show that it is possible to reproduce theoretical
+results on cross-sectional distributions using numerical simulation, and it is
+thus possible to solve Wicksell's Corpuscle Problem in this manner.
+
+\section{Method}
+Consider many spheres of different radii distributed randomly in space. For the
+purposes of the numerical simulation, we will consider a cube of length 20. The
+spheres were not allowed to overlap, which we ensured by placing the spheres such
+that if one sphere has vector position $\overrightarrow{\textbf{a}}$ and radius
+$r_{1}$ and the other has vector position $\overrightarrow{\textbf{b}}$ and
+radius $r_{2}$, the spheres must have positions such that:
+\begin{equation*}
+|\overrightarrow{\textbf{a}} - \overrightarrow{\textbf{b}}| > (r_{1} + r_{2})
+\end{equation*}
+Random coordinates for a sphere are drawn from a uniform distribution and
+checked against every existing sphere until a set of coordinates is drawn that
+ensures no overlap, at which point the sphere is placed in space and the process
+is repeated until all the necessary spheres have been placed.
+
+\begin{figure}[H]%[!ht]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{./../Figures/box3d.pdf}
+\caption{750 spheres of radius 0.7 distributed randomly in a cube of length 20,
+  such that no sphere is touching or overlapping another sphere. A randomly
+  oriented plane passes through the box and ``cuts'' through the
+  spheres.}\label{fig:3dplot_plane}
+\end{center}
+\end{figure}
+
+We then placed a plane into the cube, with a random orientation. The plane will
+``cut'' through many of the spheres in the cube. This is shown in
+Figure~\ref{fig:3dplot_plane}. Here we see 750 spheres, each with radius 0.7
+distributed randomly in a cube of length 20. The plane is shown in blue, and can
+be seen intersecting many of the spheres in the cube.
+
+In order to obtain the planar cross-section, we employed the spherical cap
+method \todo{cite}. If we consider a sphere with centre
+$\overrightarrow{\textbf{c}_0} = (x_0, y_0, z_0)$ and radius $R$, and a plane
+with equation $Ax + By + Cz = D$ such that $\overrightarrow{\textbf{n}} = (A, B,
+C)$ is the normal vector to the plane, then the distance from the centre of the
+circle to the closest point on the plane $p_0$ is given by $\rho$:
+\begin{equation*}
+\rho = \frac{(\overrightarrow{\textbf{c}_0} - \overrightarrow{\textbf{p}_0}) \cdot{}
+  \overrightarrow{\textbf{n}}}{|\overrightarrow{\textbf{n}}|} = \frac{Ax_0 +
+  By_0 + Cz_0 - D}{\sqrt{A^2 + B^2 + C^2}}
+\end{equation*}
+If $|\rho| < R$, then there is an intersection of the plane and the sphere. The
+radius of the circle $r$ in the planar cross-section is given by:
+\begin{equation*}
+r = \sqrt{R^2 - \rho^2}
+\end{equation*}
+And we then binned this radius to produce a histogram of the distribution of
+planar circle radii. It is also possible to recover the centre
+$\overrightarrow{\textbf{c}}$ of the circle visible on the plane using:
+\begin{equation*}
+\overrightarrow{\textbf{c}} = \overrightarrow{\textbf{c}_0} +
+\rho\frac{\overrightarrow{\textbf{n}}}{|\overrightarrow{\textbf{c}}|} = (x_0,
+y_0, z_0) + \rho\frac{(A, B, C)}{\sqrt{A^2 + B^2 + C^2}}
+\end{equation*}
+
+\begin{figure}[H]%[!ht]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{./../Figures/circles.pdf}
+\caption{Planar cross-section constructed using mock data. Spheres cut by the
+  plane appear as circles on the plane, with radius dependent on the relative
+  position of the spheres to the plane. This distribution of circles can be
+  modelled.}\label{fig:circles}
+\end{center}
+\end{figure}
+
+Figure~\ref{fig:circles} presents a planar cross-section generated using this
+method and mock data. As we see, there are a range of circular radii observed
+since even though the spheres all had the same radius, they were at different
+distances from the plane, and were thus cut at different points. The many
+observed circular radii are binned to produce a distribution.
+
+If $f(R)dR$ is the number of spheres per unit volume with radii in interval $[R,
+R + dR]$, then we can define a distribution $\phi(x)dx$ which represents the
+number of circles per unit area on the plane with radii in interval $[x,
+x+dx]$ \todo{cite}. This distribution is given by:
+\begin{equation}
+\phi(x) = \int_{x}^{\infty}\frac{xf(R)}{\sqrt{R^2 - x^2}}
+\label{eq:phi_OG}
+\end{equation}
+We can compute this integral to obtain a theoretical planar distribution for
+different starting spherical radius distributions.
+
+We first considered the case in which all the spheres had the same radius
+$R_0$. In this case, the spherical radius distribution is simply a Dirac delta
+function centred on the radius $R_0$.
+
+If we compute the integral in Equation~\ref{eq:phi_OG}, replacing $f(R)$ with
+$\delta(R-R_0)$ we find:
+\begin{equation}
+\phi(x) = \int_{x}^{\infty}\frac{x\delta(R-R_0)}{\sqrt{R^2 - x^2}} =
+\frac{xH(R_0-x)}{\sqrt{R_0^2-x^2}}
+\label{eq:phi_constant}
+\end{equation}
+where $H(R_0 - x)$ is the heaviside function, which ``turns on'' the
+distribution only for $x < R0$ as it is not possible to have a circular radius
+$x$ larger than the spherical radius. So we aim to see our experimental data
+reproduce this distribution \todo{cite}. We also investigated how changing the
+value of $R_0$ affects the experimental distribution.
+
+We next considered the case in which each sphere has a radius $R$ uniformly
+distributed in a range $R_1 < R < R_2$. In this case, we modify $f(R)$ in
+Equation~\ref{eq:phi_OG} to be:
+\begin{equation*}
+  f(R) =
+  \begin{cases}
+    1,& \text{if } R_1 < R < R_2\\
+    0,& \text{} Otherwise
+  \end{cases}
+\end{equation*}
+In this case the integral in Equation~\ref{eq:phi_OG} does not need to be
+computed with the limits shown, but instead with limits between $R_1$ and $R_2$
+since $f(R)$ is 0 otherwise:
+
+\begin{equation}
+\begin{split}
+  \phi(x) & = \int_{R_1}^{R_2}\frac{xf(R)}{\sqrt{R^2 - x^2}} \\
+  = x\ln\left(\sqrt{R_2^2 - x^2}+R_2\right) & - x\ln\left(\sqrt{R_1^2 - x^2}+R_1\right)
+\end{split}
+\end{equation}
+Since this distribution produces complex numbers for $ x < R_1$, we only
+consider the real part of this distribution, which appears to produce a peak at
+$x = R_1$.
 
@@
 
-\begin{figure}[H]%[!ht]
-\begin{center}
-\includegraphics[width=0.45\textwidth]{./../Figures/box3d_noplane.pdf}
-\caption{Illustrations, graphs, and photographs may fit across both columns, if
-  necessary. Your artwork must be in place in the article.}
-\label{fig:3dplot}
-\end{center}
-\end{figure}
-
-\begin{figure}[H]%[!ht]
-\begin{center}
-\includegraphics[width=0.45\textwidth]{./../Figures/box3d.pdf}
-\caption{Illustrations, graphs, and photographs may fit across both columns, if
-  necessary. Your artwork must be in place in the article.}
-\label{fig:3dplot_plane}
-\end{center}
-\end{figure}
-
-\begin{figure}[H]%[!ht]
-\begin{center}
-\includegraphics[width=0.45\textwidth]{./../Figures/circles.pdf}
-\caption{Illustrations, graphs, and photographs may fit across both columns, if
-  necessary. Your artwork must be in place in the article.}
-\label{fig:circles}
-\end{center}
-\end{figure}
+% \begin{figure}[H]%[!ht]
+% \begin{center}
+% \includegraphics[width=0.45\textwidth]{./../Figures/box3d_noplane.pdf}
+% \caption{Spheres of radius 0.7 distributed randomly in a cube of length 20, such
+%   that no sphere is touching or overlapping another sphere.}
+% \label{fig:3dplot}
+% \end{center}
+% \end{figure}
 
@@
 \includegraphics[width=0.45\textwidth]{./../Figures/750_01.pdf}
-\caption{Illustrations, graphs, and photographs may fit across both columns, if
-  necessary. Your artwork must be in place in the article.}
-\label{fig:size1}
+\caption{Distribution of circle radii on plane for 750 spheres of radius $0.1$
+  each. There are relatively few points since the spheres are small, so there is
+  relatively small chance that they will be cut by the plane. So only a few
+  circles are visible on the plane. The theoretical distribution is shown, with
+  the experimental data matching this distribution, showing a slow increase in
+  number or circles as radius increases.}\label{fig:size1}
 \end{center}
@@
 \includegraphics[width=0.45\textwidth]{./../Figures/750_03.pdf}
-\caption{Illustrations, graphs, and photographs may fit across both columns, if
-  necessary. Your artwork must be in place in the article.}
-\label{fig:size3}
+\caption{Distribution of circle radii on plane for 750 spheres of radius $0.3$
+  each. Compared to Figure~\ref{fig:size1}, there are many more experimental data
+  points, since it is more likely that the plane will intersect these larger
+  spheres. The experimental data more clearly resembles the theoretical
+  distribution, showing a strong increase in number of circles as radius
+  increases towards the maximum of 0.3.}\label{fig:size3}
 \end{center}
@@
 \includegraphics[width=0.45\textwidth]{./../Figures/750_07.pdf}
-\caption{Illustrations, graphs, and photographs may fit across both columns, if
-  necessary. Your artwork must be in place in the article.}
-\label{fig:size7}
+\caption{Distribution of circle radii on plane for 750 spheres of radius $0.7$
+  each. We do not observe much difference in how well the experimental data
+  resembles the theoretical distribution between this figure and
+  Figure~\ref{fig:size3}. With larger sized spheres, the simulation becomes harder
+  to run as it is more difficult to randomly place spheres in a finite space
+  without overlap.}\label{fig:size7}
 \end{center}
@@
 \includegraphics[width=0.45\textwidth]{./../Figures/750_07_random.pdf}
-\caption{Illustrations, graphs, and photographs may fit across both columns, if
-  necessary. Your artwork must be in place in the article.}
+\caption{Distribution of circle radii on plane for 750 spheres of radius $R$
+  where $0.65 < R < 0.7$. The theoretical distribution is now different,
+  although the experimental data still resembles this new distribution, showing
+  a maximum around $R = 0.7$ and a sharp decrease after this. This is likely
+  because there are more spheres with radii such that an overlap between $0$ and
+  $0.7$ is possible, and relatively few spheres with radii such that a larger
+  overlap is possible.}
 \label{fig:random}
@@
 
-\begin{figure}[H]%[!ht]
-\begin{center}
-\includegraphics[width=0.45\textwidth]{./../Figures/750_07_NoNoise.pdf}
-\caption{Illustrations, graphs, and photographs may fit across both columns, if
-  necessary. Your artwork must be in place in the article.}
-\label{fig:nonoise}
-\end{center}
-\end{figure}
+% \begin{figure}[H]%[!ht]
+% \begin{center}
+% \includegraphics[width=0.45\textwidth]{./../Figures/750_07_NoNoise.pdf}
+% \caption{Illustrations, graphs, and photographs may fit across both columns, if
+%   necessary. Your artwork must be in place in the article.}
+% \label{fig:nonoise}
+% \end{center}
+% \end{figure}
 
-\begin{figure}[H]%[!ht]
-\begin{center}
-\includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_100.pdf}
-\caption{Illustrations, graphs, and photographs may fit across both columns, if
-  necessary. Your artwork must be in place in the article.}
-\label{fig:2noise}
-\end{center}
-\end{figure}
+% \begin{figure}[H]%[!ht]
+% \begin{center}
+% \includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_100.pdf}
+% \caption{Illustrations, graphs, and photographs may fit across both columns, if
+%   necessary. Your artwork must be in place in the article.}
+% \label{fig:2noise}
+% \end{center}
+% \end{figure}
 
-\begin{figure}[H]%[!ht]
-\begin{center}
-\includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_10.pdf}
-\caption{Illustrations, graphs, and photographs may fit across both columns, if
-  necessary. Your artwork must be in place in the article.}
-\label{fig:1noise}
-\end{center}
-\end{figure}
+% \begin{figure}[H]%[!ht]
+% \begin{center}
+% \includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_10.pdf}
+% \caption{Illustrations, graphs, and photographs may fit across both columns, if
+%   necessary. Your artwork must be in place in the article.}
+% \label{fig:1noise}
+% \end{center}
+% \end{figure}
+
+\begin{figure*}[ht!]
+  \centering
+  \subfloat[Noise 2 orders of magnitude smaller than radius]
+  {\includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_100.pdf}
+  \label{fig:2noise}}
+  \centering
+  \subfloat[Noise 1 order of magnitude smaller than radius]
+  {\includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_10.pdf}
+  \label{fig:1noise}}
+  \caption{Distribution of circle radii on plane for 750 balls of radius $0.7$
+    each. Each recorded radius has a random noise added to it in order to
+    determine how sensitive the data is to experimental
+    error. Figure~\ref{fig:2noise} shows the distribution for an added noise 2
+    orders of magnitude smaller than the recorded radius, while
+    Figure~\ref{fig:1noise} is the same for noise 1 order of magnitude smaller. As
+    we can see, the experimental data very resembles the theoretical
+    distribution when noise of 2 orders of magnitude smaller are added. But this
+    is not true when noise of 1 order of magnitude smaller is added, implying
+    the data is very sensitive to experimental data.}
+  \label{fig:noiseplots}
+\end{figure*}
 

### 2020-05-24 Paper/main.tex
Mid way through results section

@@
 \begin{abstract}
-  Text
+  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
+  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
+  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
+  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
+  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
+  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
+  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
+  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
+  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
+  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
+  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
 \end{abstract}
@@
 \section{Method}
+
 Consider many spheres of different radii distributed randomly in space. For the
@@
 \includegraphics[width=0.45\textwidth]{./../Figures/box3d.pdf}
-\caption{750 spheres of radius 0.7 distributed randomly in a cube of length 20,
+\caption{$750$ spheres of radius 0.7 distributed randomly in a cube of length 20,
   such that no sphere is touching or overlapping another sphere. A randomly
@@
 ``cut'' through many of the spheres in the cube. This is shown in
-Figure~\ref{fig:3dplot_plane}. Here we see 750 spheres, each with radius 0.7
+Figure~\ref{fig:3dplot_plane}. Here we see $750$ spheres, each with radius 0.7
 distributed randomly in a cube of length 20. The plane is shown in blue, and can
@@
 
-\section{Results}
-Text
+\section{Results and Discussion}
 
-% \begin{figure}[H]%[!ht]
-% \begin{center}
-% \includegraphics[width=0.45\textwidth]{./../Figures/box3d_noplane.pdf}
-% \caption{Spheres of radius 0.7 distributed randomly in a cube of length 20, such
-%   that no sphere is touching or overlapping another sphere.}
-% \label{fig:3dplot}
-% \end{center}
-% \end{figure}
+We found that for both the case of the spheres of constant radius, and the case
+of the spheres of varying radius, the experimental data reproduced a
+distribution in the same shape as the theoretical distribution.
+
+We first investigated the case where we placed $750$ spheres of radius $0.1$
+each in a cube of length $20$. In this case we found that a plane in a random
+orientation intersects very few spheres, since the spheres are very small. The
+planar distribution is presented in Figure~\ref{fig:size1}.
 
@@
 \includegraphics[width=0.45\textwidth]{./../Figures/750_01.pdf}
-\caption{Distribution of circle radii on plane for 750 spheres of radius $0.1$
+\caption{Distribution of circle radii on plane for $750$ spheres of radius $0.1$
   each. There are relatively few points since the spheres are small, so there is
@@
 
+We observe relatively few experimental data points, as there were relatively few
+intersections with the plane. This was likely because the spheres' radii were
+very small compared to box length and there were relatively few spheres. While
+the theoretical distribution shows a strong increase near $0.1$, this is not
+evident from the experimental data. We also see that there is a lot of variance
+between the points so the slow rise evident in the theoretical distribution is
+not clear in the experimental data. It is thus necessary that we have more
+spheres that intersect with the plane, in order to obtain a larger data-set.
+
+We found that increasing the spheres' size or placing more spheres in the box,
+or making the box length smaller, are all good methods of increasing the number
+of intersections we observe, as they all increase the likelihood of intersection
+by increasing the ratio of sphere occupied space to total box space. We thus
+next used $750$ spheres of radius $0.3$ each. The planar cross-sectional
+distribution found is presented in Figure~\ref{fig:size3}.
+
 \begin{figure}[H]%[!ht]
@@
 \includegraphics[width=0.45\textwidth]{./../Figures/750_03.pdf}
-\caption{Distribution of circle radii on plane for 750 spheres of radius $0.3$
+\caption{Distribution of circle radii on plane for $750$ spheres of radius $0.3$
   each. Compared to Figure~\ref{fig:size1}, there are many more experimental data
@@
 
+In Figure~\ref{fig:size3} we see that there are clearly more experimental data
+points. This is because more spheres had intersections with the plane. Compared
+to Figure~\ref{fig:1noise}, the slow rise in the theoretical distribution is
+more closely followed by the experimental data. However, we still encounter
+significant variance and fluctuation in lower radius bins, even though the
+theoretical data is a smooth gradual increase. This is likely due to the
+relatively few number of circles populating these bins, causing greater relative
+difference between neighbouring bins. One method to solve this would be to use
+fewer bins, which would have the effect of ``summing and averaging''
+neighbouring bins so the experimental data has a smoother trend. However, this
+would also reduce the number of data points so it was not implemented in our
+investigation.
+
 \begin{figure}[H]%[!ht]
@@
 \includegraphics[width=0.45\textwidth]{./../Figures/750_07.pdf}
-\caption{Distribution of circle radii on plane for 750 spheres of radius $0.7$
+\caption{Distribution of circle radii on plane for $750$ spheres of radius $0.7$
   each. We do not observe much difference in how well the experimental data
@@
 \includegraphics[width=0.45\textwidth]{./../Figures/750_07_random.pdf}
-\caption{Distribution of circle radii on plane for 750 spheres of radius $R$
-  where $0.65 < R < 0.7$. The theoretical distribution is now different,
+\caption{Distribution of circle radii on plane for $750$ spheres of radius $R$
+  where $0.65 < R < 0.75$. The theoretical distribution is now different,
   although the experimental data still resembles this new distribution, showing
@@
   \label{fig:1noise}}
-  \caption{Distribution of circle radii on plane for 750 balls of radius $0.7$
+  \caption{Distribution of circle radii on plane for $750$ balls of radius $0.7$
     each. Each recorded radius has a random noise added to it in order to
@@
 
-\section{Discussion and Summary}
+\section{Conclusions}
 Text
@@
 %
-\appendices{}
-\section{Appendix Name}
-Text
+% \appendices{}
+% \section{Appendix Name}
+% Text
 

### 2020-05-24 Paper/main.tex
First draft completed

@@
 \begin{abstract}
-  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
-  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
-  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
-  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
-  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
-  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
-  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
-  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
-  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
-  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
-  Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
+  In this paper we present a 3-dimensional numerical simulation demonstrating
+  that it is possible to reproduce the known planar cross-section distributions
+  for Wicksell's Corpuscle Problem, thereby recovering 3D particle size
+  distributions from 2D cross-sections. We investigate the effects of different
+  particle sizes on the experimental data, and show this method is accurate for
+  2 different starting 3D size distributions. We also present our findings on
+  how sensitive this method is to experimental data and discuss its efficacy in
+  a real world application such as identifying a material using a planar
+  cross-section image from a microscope.
 \end{abstract}
@@
 
-\begin{figure}[H]%[!ht]
+\begin{figure}%[H]%[!ht]
 \begin{center}
@@
 
-\begin{figure}[H]%[!ht]
+The sharp rise in the theoretical distribution close to the maximum radius is
+also clear in the experimental data. It can be understood intuitively that we
+expect to see more cross-sections with radius close to radius of the spheres
+since there is a greater probability of intersection with the centre of a sphere
+than any other point on the sphere.
+
+Increasing the size of the spheres further to a radius of $0.7$, we might
+initially expect the experimental data to resemble the theoretical distribution
+even more closely, but this is not what we see. Figure~\ref{fig:size7} presents
+the planar distribution for $750$ spheres of radius $0.7$ each.
+
+\begin{figure}%[H]%[!ht]
 \begin{center}
@@
 
-\begin{figure}[H]%[!ht]
+In Figure~\ref{fig:size7}, we see a similar experimental distribution to that of
+Figure~\ref{fig:size3}, as opposed to a distribution that more closely resembles
+the theoretical distribution. While initially this may seem contrary to the
+notion that increasing size of spheres would increase the number of
+intersections and thus give a better distribution, this may simply be due to the
+fact that increasing the size of the spheres beyond a certain radius does not
+provide continually better results. We observe a similar number of intersections
+as the case with spheres of radius $0.3$, and thus it is possible to conclude
+that the best experimental distribution is found for a spherical size that
+ensures a significant number of intersections. Though continually increasing
+spherical size provides diminishing returns.
+
+Indeed, we found that making the sphere sizes much larger made the placing of
+the spheres in a finite space more difficult, and exponentially increased the
+time complexity of the placing algorithm. This is because if the placed spheres
+are too large, while it is initially easy to place spheres, as more are placed,
+more coordinates must be randomly drawn before one if found for the next sphere
+to be placed into. It is also possible that the algorithm never finds a possible
+coordinate for later spheres. One possible solution to this may be to use a
+better placing algorithm. Choosing a tight packing algorithm \todo{cite} would
+maximise the number of spheres of a given radius that can be placed. However,
+this would likely result in a less than random distribution of spheres if the
+spheres are all of identical sizes. This would likely cause some systematic
+error in the data, and so it was not investigated here. If we randomised the
+sizes of the spheres as we do in the next part of the investigation, the problem
+become significantly more complicated. Tight packing algorithms for irregular
+shaped objects are very difficult to create and computationally expensive
+\todo{cite}.
+
+We next randomised the radius of each sphere to be in the range $0.65 < R <
+0.75$. The experimental data for this simulation is presented in
+Figure~\ref{fig:random}.
+
+\begin{figure}%[H]%[!ht]
 \begin{center}
@@
 
-% \begin{figure}[H]%[!ht]
-% \begin{center}
-% \includegraphics[width=0.45\textwidth]{./../Figures/750_07_NoNoise.pdf}
-% \caption{Illustrations, graphs, and photographs may fit across both columns, if
-%   necessary. Your artwork must be in place in the article.}
-% \label{fig:nonoise}
-% \end{center}
-% \end{figure}
+Figure~\ref{fig:random} presents the experimental data for 750 spheres with each
+sphere having a radius $0.65 < R < 0.75$. As we can see, the theoretical
+distribution has a very different shape to the case of constant sphere
+radius. We see that the theoretical distribution has a sharp peak centred around
+(but not precisely at) $0.65$, the lower limit of the uniform range the radii
+were drawn from, and a sharp decrease after this point. This is likely due to
+the higher number of spheres available in the box which could be intersected so
+as to show a planar cross-section with radius $\approx 0.65$. In a range of
+radii between $0.65 < R < 0.75$, all the spheres in the box can be intersected
+so as to produce a circle of radius $0.65$, but there will be fewer spheres
+which can be intersected to produce a circle of radius greater than this. So a
+peak at this point and then a sharp decrease is expected.
 
-% \begin{figure}[H]%[!ht]
-% \begin{center}
-% \includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_100.pdf}
-% \caption{Illustrations, graphs, and photographs may fit across both columns, if
-%   necessary. Your artwork must be in place in the article.}
-% \label{fig:2noise}
-% \end{center}
-% \end{figure}
+The experimental data resembles the theoretical distribution, clearly showing a
+peak and sharp decrease after. However, we also see that there is significant
+variance between bins, and there is a large scatter around the theoretical
+data. As explained for Figure~\ref{fig:size3}, it would be possible to reduce
+this fluctuation by using fewer bins, at the cost of having fewer data
+points. With a more powerful computer, or if the simulation is optimised and
+written with a compiled language, there is also scope for significantly
+increasing the size and number of spheres used, which would provide better
+experimental data.
 
-% \begin{figure}[H]%[!ht]
-% \begin{center}
-% \includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_10.pdf}
-% \caption{Illustrations, graphs, and photographs may fit across both columns, if
-%   necessary. Your artwork must be in place in the article.}
-% \label{fig:1noise}
-% \end{center}
-% \end{figure}
+While there is significant fluctuation and scatter in all of the simulations
+presented so far, the shapes of the distributions were mostly clear, and they
+resembled the theoretical distribution. However, if the system is very sensitive
+to experimental error, it may be difficult to identify distribution shapes, and
+thus prevent us from properly identifying the starting distribution of spherical
+radii. We therefore introduced some additional random error into the data. After
+the radii of the circles on the plane are calculated, a small random number is
+added to each radius. The random number is drawn from a uniform distribution in
+the range $[\frac{-r}{n}, \frac{r}{n}]$, where r is the circle's radius and n is
+the number of orders of magnitude we wish to choose the errors. We tested the
+system with errors 2 orders of magnitude smaller than the radii and 1 order of
+magnitude smaller than the radii. This is presented in
+Figure~\ref{fig:noiseplots}.
 
-\begin{figure*}[ht!]
+\begin{figure*}%[ht!]
   \centering
@@
   \label{fig:1noise}}
-  \caption{Distribution of circle radii on plane for $750$ balls of radius $0.7$
+  \caption{Distribution of circle radii on plane for $750$ spheres of radius $0.7$
     each. Each recorded radius has a random noise added to it in order to
@@
 
+Figure~\ref{fig:2noise} presents the distribution for $750$ spheres or radius
+$0.7$ each, with an added ``noise'' that is 2 orders of magnitude smaller than
+each measured radius. We can see that the experimental data looks very similar
+to the data presented in Figure~\ref{fig:size7}. The shape of the distribution
+is also very clear and resembles the theoretical distribution.
+
+Figure~\ref{fig:1noise} presents the same simulation but with an added noise
+that is 1 order of magnitude smaller than each measured radius. Here we can see
+that the experimental data is unrecognisable, and the shape of the distribution
+is no longer clear. We thus conclude that the system is very sensitive to noise
+greater than 2 orders of magnitude compared to the measured data.
+
+However, it would be more prudent to use a Gaussian distribution to draw the
+values of the noise. This is because it is likely that the many sources of error
+possible in an experimental measurement of particle cross-sections in a material
+will be convoluted together into a Gaussian distribution of errors due to the
+central limit theorem \todo{cite}.
+
 \section{Conclusions}
-Text
+In this investigation we showed that it is possible to reproduce expected planar
+distributions for the Corpuscle Problem with a 3-dimensional numerical
+simulation of spheres distributed randomly in space, where a plane oriented
+randomly intersects the spheres. We investigated how effective this method of
+simulation is for different particle sizes, and showed that while initially
+larger particles provide better data since they allow for more intersections,
+continually increasing particle size becomes ineffective and computationally
+expensive.
+
+We showed it was possible to reproduce the expected planar distributions for two
+starting spherical radii distributions: a Dirac delta distribution, in which all
+the spheres have the same radius, and a bounded uniform distribution, in which
+all the spheres' radii are drawn randomly from a uniform distribution. Both
+produce different shaped planar distributions but both provide data that
+resembles the theoretical distributions.
+
+We also investigated how sensitive this method is to experimental error. We
+introduced some random noise into the system from a random uniform distribution
+and demonstrated that the system is very sensitive to noise greater than two
+orders of magnitude relative to measured data. Thus it is important for any
+experimentalist making measurements of particle cross-sections in a material to
+be very careful with error handling, as any error larger than 2 orders of
+magnitude compared to measured data will result in great difficulty in
+reproducing the spherical radii distributions.
+
+We therefore showed in this investigation that it is possible to use the known
+solutions to Wicksell's Corpuscle Problem to better identify and classify
+materials by using planar measurements to gain information about 3D particle
+distributions.
 

### 2020-05-24 Paper/main.tex
Moved figures into better positions

@@
 
-\usepackage[caption=false]{subfig}
+\usepackage{blindtext, subfig}
+\usepackage{dblfloatfix}
+
+% \usepackage[caption=false]{subfig}
 \usepackage{todonotes}
@@
 \markboth{PHYS6017 Computer Techniques in Physics Report 2, May 2020}
-% do not delete next lines
 {Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
@@
 
-Increasing the size of the spheres further to a radius of $0.7$, we might
-initially expect the experimental data to resemble the theoretical distribution
-even more closely, but this is not what we see. Figure~\ref{fig:size7} presents
-the planar distribution for $750$ spheres of radius $0.7$ each.
-
 \begin{figure}%[H]%[!ht]
@@
 \end{figure}
+
+\begin{figure}[H]%[!ht]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{./../Figures/750_07_random.pdf}
+\caption{Distribution of circle radii on plane for $750$ spheres of radius $R$
+  where $0.65 < R < 0.75$. The theoretical distribution is now different,
+  although the experimental data still resembles this new distribution, showing
+  a maximum around $R = 0.7$ and a sharp decrease after this. This is likely
+  because there are more spheres with radii such that an overlap between $0$ and
+  $0.7$ is possible, and relatively few spheres with radii such that a larger
+  overlap is possible.}
+\label{fig:random}
+\end{center}
+\end{figure}
+
+\begin{figure*}[ht!]
+  \centering
+  \subfloat[Noise 2 orders of magnitude smaller than radius]
+  {\includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_100.pdf}
+  \label{fig:2noise}}
+  \centering
+  \subfloat[Noise 1 order of magnitude smaller than radius]
+  {\includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_10.pdf}
+  \label{fig:1noise}}
+  \caption{Distribution of circle radii on plane for $750$ spheres of radius $0.7$
+    each. Each recorded radius has a random noise added to it in order to
+    determine how sensitive the data is to experimental
+    error. Figure~\ref{fig:2noise} shows the distribution for an added noise 2
+    orders of magnitude smaller than the recorded radius, while
+    Figure~\ref{fig:1noise} is the same for noise 1 order of magnitude smaller. As
+    we can see, the experimental data very resembles the theoretical
+    distribution when noise of 2 orders of magnitude smaller are added. But this
+    is not true when noise of 1 order of magnitude smaller is added, implying
+    the data is very sensitive to experimental data.}
+  \label{fig:noiseplots}
+\end{figure*}
+
+Increasing the size of the spheres further to a radius of $0.7$, we might
+initially expect the experimental data to resemble the theoretical distribution
+even more closely, but this is not what we see. Figure~\ref{fig:size7} presents
+the planar distribution for $750$ spheres of radius $0.7$ each.
 
@@
 Figure~\ref{fig:random}.
-
-\begin{figure}%[H]%[!ht]
-\begin{center}
-\includegraphics[width=0.45\textwidth]{./../Figures/750_07_random.pdf}
-\caption{Distribution of circle radii on plane for $750$ spheres of radius $R$
-  where $0.65 < R < 0.75$. The theoretical distribution is now different,
-  although the experimental data still resembles this new distribution, showing
-  a maximum around $R = 0.7$ and a sharp decrease after this. This is likely
-  because there are more spheres with radii such that an overlap between $0$ and
-  $0.7$ is possible, and relatively few spheres with radii such that a larger
-  overlap is possible.}
-\label{fig:random}
-\end{center}
-\end{figure}
 
@@
 Figure~\ref{fig:noiseplots}.
-
-\begin{figure*}%[ht!]
-  \centering
-  \subfloat[Noise 2 orders of magnitude smaller than radius]
-  {\includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_100.pdf}
-  \label{fig:2noise}}
-  \centering
-  \subfloat[Noise 1 order of magnitude smaller than radius]
-  {\includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_10.pdf}
-  \label{fig:1noise}}
-  \caption{Distribution of circle radii on plane for $750$ spheres of radius $0.7$
-    each. Each recorded radius has a random noise added to it in order to
-    determine how sensitive the data is to experimental
-    error. Figure~\ref{fig:2noise} shows the distribution for an added noise 2
-    orders of magnitude smaller than the recorded radius, while
-    Figure~\ref{fig:1noise} is the same for noise 1 order of magnitude smaller. As
-    we can see, the experimental data very resembles the theoretical
-    distribution when noise of 2 orders of magnitude smaller are added. But this
-    is not true when noise of 1 order of magnitude smaller is added, implying
-    the data is very sensitive to experimental data.}
-  \label{fig:noiseplots}
-\end{figure*}
 
@@
 
-% if have a single appendix:
-%\appendix[Proof of the Zonklar Equations]
-% or
-%\appendix  % for no appendix heading
-% do not use \section anymore after \appendix, only \section*
-% is possibly needed
-
-% use appendices with more than one appendix
-% then use \section to start each appendix
-% you must declare a \section before using any
-% \subsection or using \label (\appendices by itself
-% starts a section numbered zero.)
-%
-% \appendices{}
-% \section{Appendix Name}
-% Text
-
 \printbibliography{}

### 2020-05-24 Paper/main.tex
added some citations

@@
 
-% \bibliography{example_bib.bib}
+\bibliography{ParticleSizeDistribution.bib}
 
@@
 sections is a well known problem called Wicksell's Corpuscle Problem
-\todo{cite}, named after S. D. Wicksell, who solved the problem in 1925. With
+\cite{DWicksell}, named after S. D. Wicksell, who solved the problem in 1925. With
 this solution, it is possible to determine the original distribution of
@@
 particle sizes in a solid from its observed cross-section, allowing us to
-identify and classify materials better \todo{nasa}.
+identify and classify materials better \cite{Cuzzi2016}.
 
@@
 In order to obtain the planar cross-section, we employed the spherical cap
-method \todo{cite}. If we consider a sphere with centre
+method \cite{Sykes1922}. If we consider a sphere with centre
 $\overrightarrow{\textbf{c}_0} = (x_0, y_0, z_0)$ and radius $R$, and a plane
@@
 number of circles per unit area on the plane with radii in interval $[x,
-x+dx]$ \todo{cite}. This distribution is given by:
+x+dx]$ \cite{Kiderlen2011}. This distribution is given by:
 \begin{equation}
@@
 $x$ larger than the spherical radius. So we aim to see our experimental data
-reproduce this distribution \todo{cite}. We also investigated how changing the
+reproduce this distribution. We also investigated how changing the
 value of $R_0$ affects the experimental distribution.
@@
 coordinate for later spheres. One possible solution to this may be to use a
-better placing algorithm. Choosing a tight packing algorithm \todo{cite} would
+better placing algorithm. Choosing a tight packing algorithm %\cite{Chen2001} would
 maximise the number of spheres of a given radius that can be placed. However,
@@
 will be convoluted together into a Gaussian distribution of errors due to the
-central limit theorem \todo{cite}.
+central limit theorem \cite{Islam2018}.
 

### 2020-05-24 Paper/main.tex
Added all citations

@@
 $x$ larger than the spherical radius. So we aim to see our experimental data
-reproduce this distribution. We also investigated how changing the
+reproduce this distribution \cite{Kong2005}. We also investigated how changing the
 value of $R_0$ affects the experimental distribution.
@@
 coordinate for later spheres. One possible solution to this may be to use a
-better placing algorithm. Choosing a tight packing algorithm %\cite{Chen2001} would
+better placing algorithm. Choosing a tight packing algorithm \cite{Chen2001} would
 maximise the number of spheres of a given radius that can be placed. However,
@@
 shaped objects are very difficult to create and computationally expensive
-\todo{cite}.
+\cite{Ma2018}.
 
@@
 will be convoluted together into a Gaussian distribution of errors due to the
-central limit theorem \cite{Islam2018}.
+central limit theorem \cite{Islam2018}. Thus, it would be necessary for any
+experimentalist attempting to carry out a similar investigation with real
+materials, perhaps to determine porosity \cite{Lekakh}, to carefully consider
+all errors in measurements.
 
@@
 
-\printbibliography{}
+\printbibliography
+
 \end{document}

### 2020-05-24 Paper/main.tex
Fixed typos

@@
 this solution, it is possible to determine the original distribution of
-spherical particles. Thus, it is possible to determmine the distribution of
+spherical particles. Thus, it is possible to determine the distribution of
 particle sizes in a solid from its observed cross-section, allowing us to
@@
 \end{equation}
-where $H(R_0 - x)$ is the heaviside function, which ``turns on'' the
+where $H(R_0 - x)$ is the Heaviside function, which ``turns on'' the
 distribution only for $x < R0$ as it is not possible to have a circular radius

### 2020-05-31 Paper/main.tex
Minor changes

@@
 distribution of its constituent particle sizes. However, direct observation of
-the particles so as to construct a distribution is often impossible. Using a
-modern microscope or laser imaging techniques, it is possible to observe
-particles in a cross-section of material. But the observed radii of particles in
-this cross-section do not necessarily correspond directly to the radii of the
-particles in the material, since the plane of the cross-section is not
-necessarily oriented such that the observed particles lie exactly on the
-plane. Thus, it becomes difficult to relate the observed distribution of
-particle sizes in the plane to the real distribution of particle sizes in the
-material.
+the particles is often impossible. Using a modern microscope or laser imaging
+techniques, it is possible to observe particles in a cross-section of
+material. But the observed radii of particles in this cross-section do not
+necessarily correspond directly to the radii of the particles in the material,
+since the plane is not oriented such that it passes through the centre of all
+observed particles. Thus, it becomes difficult to relate the observed
+distribution of particle sizes in the plane to the real distribution of particle
+sizes in the material.
 
@@
 sections is a well known problem called Wicksell's Corpuscle Problem
-\cite{DWicksell}, named after S. D. Wicksell, who solved the problem in 1925. With
-this solution, it is possible to determine the original distribution of
-spherical particles. Thus, it is possible to determine the distribution of
+\cite{DWicksell}, named after S. D. Wicksell, who solved the problem in
+1925. With this solution, it is possible to determine the distribution of
 particle sizes in a solid from its observed cross-section, allowing us to
@@
 In this paper we aim to show that it is possible to reproduce theoretical
-results on cross-sectional distributions using numerical simulation, and it is
+results for cross-sectional distributions using numerical simulation, and it is
 thus possible to solve Wicksell's Corpuscle Problem in this manner.
@@
 
-Consider many spheres of different radii distributed randomly in space. For the
-purposes of the numerical simulation, we will consider a cube of length 20. The
-spheres were not allowed to overlap, which we ensured by placing the spheres such
-that if one sphere has vector position $\overrightarrow{\textbf{a}}$ and radius
-$r_{1}$ and the other has vector position $\overrightarrow{\textbf{b}}$ and
-radius $r_{2}$, the spheres must have positions such that:
+The numerical simulation of the 3D particle distribution was done using
+Python. It looked at many spheres of different radii, distributed randomly in
+space with a given "box of length 20. The spheres were not allowed to overlap,
+which we ensured by placing the spheres such that if one sphere has vector
+position $\overrightarrow{\textbf{a}}$ and radius $r_{1}$ and the other has
+vector position $\overrightarrow{\textbf{b}}$ and radius $r_{2}$, the spheres
+must have positions such that:
 \begin{equation*}
@@
 \end{equation*}
-Random coordinates for a sphere are drawn from a uniform distribution and
-checked against every existing sphere until a set of coordinates is drawn that
-ensures no overlap, at which point the sphere is placed in space and the process
-is repeated until all the necessary spheres have been placed.
+Random coordinates for a sphere were drawn from a uniform distribution and
+checked against every existing sphere until a set of coordinates was drawn that
+ensures no overlap, at which point the sphere was placed in space and the process
+was repeated until all the necessary spheres have been placed.
 
@@
 \caption{$750$ spheres of radius 0.7 distributed randomly in a cube of length 20,
-  such that no sphere is touching or overlapping another sphere. A randomly
-  oriented plane passes through the box and ``cuts'' through the
+  such that no sphere is touching or overlapping another sphere. A horizontal
+  plane, in blue, passes through the box and ``cuts'' through the
   spheres.}\label{fig:3dplot_plane}
@@
 
-We then placed a plane into the cube, with a random orientation. The plane will
-``cut'' through many of the spheres in the cube. This is shown in
-Figure~\ref{fig:3dplot_plane}. Here we see $750$ spheres, each with radius 0.7
-distributed randomly in a cube of length 20. The plane is shown in blue, and can
-be seen intersecting many of the spheres in the cube.
+We then placed a plane into the cube, with a random orientation, which
+``cuts'' through many of the spheres in the cube. This is shown in
+Figure~\ref{fig:3dplot_plane}, where we see a plane (in blue) intersecting 750
+spheres of constant radius, distributed at random in a box.
 
@@
 C)$ is the normal vector to the plane, then the distance from the centre of the
-circle to the closest point on the plane $p_0$ is given by $\rho$:
+circle to the closest point on the plane $\overrightarrow{\textbf{p}_0}$ is given by $\rho$:
 \begin{equation*}
@@
   plane appear as circles on the plane, with radius dependent on the relative
-  position of the spheres to the plane. This distribution of circles can be
-  modelled.}\label{fig:circles}
+  position of the spheres to the plane. This distribution of the radii of the
+  circles can be modelled.}\label{fig:circles}
 \end{center}
@@
 where $H(R_0 - x)$ is the Heaviside function, which ``turns on'' the
-distribution only for $x < R0$ as it is not possible to have a circular radius
+distribution only for $x < R_0$ as it is not possible to have a circular radius
 $x$ larger than the spherical radius. So we aim to see our experimental data
-reproduce this distribution \cite{Kong2005}. We also investigated how changing the
-value of $R_0$ affects the experimental distribution.
+reproduce this distribution \cite{Kong2005}. We also investigated how changing
+the size of the spheres used in the simulation affects the experimental data.
 
@@
 
-We next randomised the radius of each sphere to be in the range $0.65 < R <
-0.75$. The experimental data for this simulation is presented in
-Figure~\ref{fig:random}.
-
 Figure~\ref{fig:random} presents the experimental data for 750 spheres with each

### 2020-09-03 Paper/main.tex
Changed location of figures for paper

@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{./../Figures/box3d.pdf}
+\includegraphics[width=0.45\textwidth]{images/box3d.pdf}
 \caption{$750$ spheres of radius 0.7 distributed randomly in a cube of length 20,
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{./../Figures/circles.pdf}
+\includegraphics[width=0.45\textwidth]{images/circles.pdf}
 \caption{Planar cross-section constructed using mock data. Spheres cut by the
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{./../Figures/750_01.pdf}
+\includegraphics[width=0.45\textwidth]{images/750_01.pdf}
 \caption{Distribution of circle radii on plane for $750$ spheres of radius $0.1$
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{./../Figures/750_03.pdf}
+\includegraphics[width=0.45\textwidth]{images/750_03.pdf}
 \caption{Distribution of circle radii on plane for $750$ spheres of radius $0.3$
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{./../Figures/750_07.pdf}
+\includegraphics[width=0.45\textwidth]{images/750_07.pdf}
 \caption{Distribution of circle radii on plane for $750$ spheres of radius $0.7$
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{./../Figures/750_07_random.pdf}
+\includegraphics[width=0.45\textwidth]{images/750_07_random.pdf}
 \caption{Distribution of circle radii on plane for $750$ spheres of radius $R$
@@
   \subfloat[Noise 2 orders of magnitude smaller than radius]
-  {\includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_100.pdf}
+  {\includegraphics[width=0.45\textwidth]{images/750_07_Noise_100.pdf}
   \label{fig:2noise}}
@@
   \subfloat[Noise 1 order of magnitude smaller than radius]
-  {\includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_10.pdf}
+  {\includegraphics[width=0.45\textwidth]{images/750_07_Noise_10.pdf}
   \label{fig:1noise}}
